### 2014-11-11 tex/bisimulation.tex
Fixed corollaries

\begin{theorem}
\label{th:bisim}
The relation $\sqsubset$ is a bisimulation: $\sqsubset\ \subseteq\ \sim$
\end{theorem}
\begin{proof}
By definition of the bisimilarity relation. All of the common rules
make no changes to the heap, so $P \subset q$ is included in the
functional. The other transition relations are supported by lemmas
such as \lemref{lem:access}.
\end{proof}

The notion $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
the $n$-step successor of $p$, if it exists, and $q
\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
soundness are readily established by \thref{th:bisim} and inducting
over $n$.

\begin{corollary}[$\rsym$ is complete]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
$$
\forall p^\prime\ (p \stackrel{n}{\rgse} p^\prime \Rightarrow \exists q^\prime\ (q \stackrel{n}{\rsym} q^\prime \wedge p^\prime \sqsubset q^\prime))
$$
\end{corollary}

\begin{corollary}[$\rsym$ is sound]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
$$
\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime))
$$
\end{corollary}

>>>>

\begin{theorem}
\label{th:bisim}
The relation $\sqsubset$ is a bisimulation: $\sqsubset\ \subseteq\ \sim$
\end{theorem}
\begin{proof}
By definition of the bisimilarity relation. All of the common rules
make no changes to the heap, so $P \sqsubset q$ is included in the
functional. The other transition relations are supported by lemmas
such as \lemref{lem:access}.
\end{proof}

The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
the $n$-step successor of $p$, if it exists, and $q
\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
soundness are readily established by \thref{th:bisim} and inducting
over $n$.

\begin{corollary}[$\rsym$ is complete]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then for any $p \in P$
$$
\forall p^\prime\ (p \stackrel{n}{\rgse} p^\prime \Rightarrow \exists q^\prime\ (q \stackrel{n}{\rsym} q^\prime \wedge p^\prime \sqsubset q^\prime))
$$
\end{corollary}

\begin{corollary}[$\rsym$ is sound]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
$$
\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p \in P\ (\exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime)))
$$
\end{corollary}
